The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-10 SI.tex
SI cleanup

\subsection{\texttt{is\_busy} for orchestrating order of operations}

@@

In order to know how long to wait, all \yaq{} daemons provide a message called
“is\_busy”, which returns "true" while the long running action
is not complete, and "false" once it is finished. Additionally,
multiple clients can communicate with the same daemon si-
multaneously. A complex instrument may involve multiple
operators watching sensor data in real time, while one pro-
gram is orchestrating the hardware and recording the data.

\subsection{Raster Script}

@@

The Wright Group uses a purpose-build graphical program to perform data acquisition.
All of the hardware used is controlled via \yaq{}.
Data is collected using Bluesky, which runs in a background process.

>>>>

\subsection{\texttt{is\_busy} for ensuring order of operations}

@@

In order to know how long to wait, all \yaq{} daemons provide a message called “is\_busy”, which returns "true" while the long running action is not complete, and "false" once it is finished.
Additionally, multiple clients can communicate with the same daemon simultaneously. A complex instrument may involve multiple operators watching sensor data in real time, while one program is orchestrating the hardware and recording the data.

Script writers may simply wait for ``is\_busy'' to return ``false''.

\begin{codefragment}{Python}
import yaqc
import time
motor = yaqc.Client(port=38000)
motor.set_position(500)  # initiate a long motor motion
while motor.is_busy():
    time.sleep(0.001)
print("done")  # will only print when motion is complete
\end{codefragment}

This same pattern exists for sensors and more complex peripherals.

\clearpage
\subsection{Raster Script}

@@

The Wright Group uses a purpose-built graphical program to perform data acquisition.
All of the hardware used is controlled via \yaq{}.
Data is collected using Bluesky, which runs in a background process.
